```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

library(lubridate)

library(data.table)

library(stringr)
```

# Izmir Fish Price Analysis

## How's the data?

Firstly, we will analyze the data for determine data structure, format, size and data defects. 


```{r }


fish_price=read.csv(file = 'https://raw.githubusercontent.com/pjournal/mef05-ustame/gh-pages/balik_hal_fiyatlari.csv',
                    stringsAsFactors = FALSE, header = TRUE,sep = ";", encoding="UTF-8")

head(fish_price)

summary(fish_price)
```

## Basic Exploration

### Min-Max Fish 


In 2021, We can determine the cheapest fish all year. First of all, we calculate the average seasonal price by "MAL_ADI".
We are taking action to determine which fish is suitable in this year.


**1. We can see that fish having the 5 highest volatile price.  ` r the_highest_fish ` **

```{r the_highest_fish }
fish_price %>%filter(MAL_TURU=='BALIK') %>%
    mutate (ay=lubridate::month(TARIH),daily_change=(AZAMI_UCRET-ASGARI_UCRET),daily_avg=(AZAMI_UCRET+ASGARI_UCRET)/2) %>%
    mutate(avg_change=(daily_change/2)/daily_avg*100) %>% group_by(MAL_ADI) %>%
    summarise(avg_seasonal_change=mean(avg_change),avg_seasonal=mean(daily_avg)) %>%
    arrange(desc(avg_seasonal_change)) %>% head(5)

```

**2. We investigate the highest volatile price of fish "MERCAN (BÜYÜKBOY)" **

When we examine the average price distribution of "MERCAN (BÜYÜKBOY)" fish by months.

```{r mercan }
 
mercan=fish_price %>% filter(MAL_ADI=="MERCAN (BÜYÜKBOY)") %>% 
  mutate (ay=lubridate::month(TARIH),daily_change=(AZAMI_UCRET-ASGARI_UCRET),daily_avg=(AZAMI_UCRET+ASGARI_UCRET)/2)

  boxplot(daily_avg~ay,
          data=mercan,
          main="Mercan Data",
          xlab="Month Number",
          ylab="Daily Average",
          col="orange",
          border="brown"
  )  
  
```

It can be purchased at an suitable price in the first 4 months "MERCAN" average.

**3. We can see that fish having the 5 lowest volatile price. ` r the_lowest_fish` **

```{r the_lowest_fish }
fish_price %>%filter(MAL_TURU=='BALIK') %>%
    mutate (ay=lubridate::month(TARIH),daily_change=(AZAMI_UCRET-ASGARI_UCRET),daily_avg=(AZAMI_UCRET+ASGARI_UCRET)/2) %>%
    mutate(avg_change=(daily_change/2)/daily_avg*100) %>% group_by(MAL_ADI) %>%
    summarise(avg_seasonal_change=mean(avg_change),avg_seasonal=mean(daily_avg)) %>%
    arrange(desc(avg_seasonal_change)) %>% tail(5)

```

When we examine the average price distribution of "MEZGİT (DONUK)" fish by months.

```{r mezgit }
 
mezgit=fish_price %>% filter(MAL_ADI=="MEZGİT (DONUK)") %>% 
  mutate (ay=lubridate::month(TARIH),daily_change=(AZAMI_UCRET-ASGARI_UCRET),daily_avg=(AZAMI_UCRET+ASGARI_UCRET)/2)

  boxplot(daily_avg~ay,
          data=mezgit,
          main="Mezgit Data",
          xlab="Month Number",
          ylab="Daily Average",
          col="red",
          border="brown"
  )  
  
```

Mezgit data 

```{r mezgit_data }
 
mezgit  
```

After analysis, I realized that  ""MEZGİT (DONUK)"  is not enough data becuase it just sold one day.

I eliminated data with less than 180 days of sales.



 ``` {r eliminated_data }
elimanted=fish_price %>% filter(MAL_TURU=='BALIK') %>% group_by(MAL_ADI) %>% 
  count() %>%filter(n>=180)
  
fish_prise_eliminated=fish_price %>%inner_join(elimanted,by="MAL_ADI")

str(fish_prise_eliminated)
```

Again, we determine  that fish having the 5 lowest volatile price.

``` {r lowest_volatile }
datamin=  fish_prise_eliminated %>%filter(MAL_TURU=='BALIK') %>%
    mutate (ay=lubridate::month(TARIH),daily_change=(AZAMI_UCRET-ASGARI_UCRET),daily_avg=(AZAMI_UCRET+ASGARI_UCRET)/2) %>%
    mutate(avg_change=(daily_change/2)/daily_avg*100) %>% group_by(MAL_ADI) %>%
    summarise(avg_seasonal_change=mean(avg_change),avg_seasonal=mean(daily_avg)) %>%
    arrange(desc(avg_seasonal_change)) %>% tail(5)
 
datamin 
```
"KOFANA ( DENİZ )" is the lowest volatile price. 

``` {r kofana }
kofana=fish_prise_eliminated %>% inner_join(datamin,by="MAL_ADI") %>% 
  mutate (ay=lubridate::month(TARIH),daily_change=(AZAMI_UCRET-ASGARI_UCRET),daily_avg=(AZAMI_UCRET+ASGARI_UCRET)/2)
  
  boxplot(daily_avg~ay,
          data=kofana,
          main="Kofana Data",
          xlab="Month Number",
          ylab="Daily Change",
          col="green",
          border="brown"
  )  

``` 
 
"Kofana" can be bought all season long. Because the price change is less than other fish species. 
 
 
 
 