---
title: "Netflix Analysis"
author: "Meryem Usta"
date: "07.11.2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

library(lubridate)

library(data.table)

library(stringr)

install.packages('plotrix')
library(plotrix)
```

## Netflix Data

Netflix's data contains from 6234 observations of 12 variables. Those variables are general information about programs such as title, director, cast, country.

```{r }
netflix_data=read.csv(file = 'https://github.com/ygterl/EDA-Netflix-2020-in-R/raw/master/netflix_titles.csv',
                    stringsAsFactors = FALSE, header = TRUE,sep = ",", encoding="UTF-8")
str(netflix_data)


```
 
## Basic Questions 

  1. How many programs are there by type or country ? 

All data contains two different type of programs that are Movie and TV Show.

```{r }
netflix_country=netflix_data %>%
  mutate(country=gsub("^(.*?),.*", "\\1", country)) %>% 
  filter(type=="Movie" & nchar(country)!=0 ) %>%
  group_by(country) %>%
  count() %>%
  arrange(desc(n)) %>% 
  head(5)

# This is normal pie chart
ggplot(netflix_country,aes(x='',y=n,fill=country))+
ggtitle("Most 10 Country by Movie Count")+
geom_bar(stat = "Identity",width = 2,color="White")+
coord_polar("y",start = 0) +
theme_void()

# This is normal donut chart

ggplot(netflix_country, aes(x = 2, y = n, fill = country)) +
  geom_bar(stat = "identity", color = "white") +
  coord_polar(theta = "y", start = 0)+
  theme_void()+
  xlim(0.5, 2.5)

``` 

We examine data according to country. 
 
```{r }
netflix_data %>% 
  group_by(country) %>%
  count()

```
 
 
 
 2. What kind of movies are in this data? 
 
 Top 3 kind of Movies are "Dramas", "Comedies" and "Documentaries".
 
```{r }
netflix_data %>%
  filter(type=="Movie") %>%
  mutate(kind=gsub("^(.*?),.*", "\\1", listed_in)) %>%
  group_by(kind) %>%
  count() %>% 
  arrange(desc(n))
``` 
 
 3. How many movie are there by country ? 
 
 When analysis, I relaized that 195 movies don't have country information. So, I eliminated this data.

```{r }
netflix_country = netflix_data %>%
  mutate(country=gsub("^(.*?),.*", "\\1", country)) %>% 
  filter(type=="Movie" & nchar(country)!=0 ) %>%
  group_by(country) %>% 
  count() %>%
  summarize(total_count=sum(n)) %>%
  arrange(desc(total_count)) %>%
  head(10)


netflix_country_by_year = netflix_data %>% 
  mutate(country=gsub("^(.*?),.*", "\\1", country)) %>% 
  filter(type=="Movie" & nchar(country)!=0 ) %>%
  group_by(country,release_year) %>% count() %>%
  arrange(desc(country,release_year)) 

netflix_country_by_year2= netflix_country_by_year %>% inner_join(netflix_country,by="country")
netflix_country_by_year2
``` 
 
Lets see the grap.
 
```{r }

ggplot(netflix_country_by_year2,aes(x=release_year,y=country,color=country,size=n)) + 
  geom_line() + 
  labs(title="Yıllara Göre Ülkelerin Toplam Film Sayısı",caption="Source: Netflix")
  
  
``` 
 4. How many movie did the directors make ? 
 
 This is same analysis above, but this time according to directors
 

```{r }
netflix_director = netflix_data %>%
  mutate(director=gsub("^(.*?),.*", "\\1", director)) %>% 
  filter(type=="Movie" & nchar(director)!=0 ) %>%
  group_by(director) %>% 
  count() %>%
  summarize(total_count=sum(n)) %>%
  arrange(desc(total_count)) %>%
  head(5)


netflix_director_by_year = netflix_data %>% 
  mutate(director=gsub("^(.*?),.*", "\\1", director)) %>% 
  filter(type=="Movie" & nchar(director)!=0 ) %>%
  group_by(director,release_year) %>% count() %>%
  arrange(desc(director,release_year)) 

netflix_director_by_year2= netflix_director_by_year %>% inner_join(netflix_director,by="director")
netflix_director_by_year2
``` 

Lets see the grap.
 
```{r }

ggplot(netflix_director_by_year2,aes(x=release_year,y=n,color=director)) + 
  geom_line() + 
  labs(title="Yıllara Göre Yönetmenlerin Film Sayısı",caption="Source: Netflix")
  
  
``` 

We saw the upper graph:
The number of films made by the directors who made the most films in the last 10 years has increased. I rearrange the formula of plot  that has data between 2005 and 2020.


 
```{r }
netflix_director_by_year2=netflix_director_by_year2 %>% filter(release_year>=2005 & release_year<=2020)

ggplot(netflix_director_by_year2,aes(x=release_year,y=n,color=director)) + 
  geom_line() + 
  labs(title="Yıllara Göre Yönetmenlerin Film Sayısı",caption="Source: Netflix") +
  expand_limits(y=0)
  
  
``` 



 4. What does situation cast ? 
 
We can find out how many movies the actors have in total.

 We can see that  7 actors of top 10  are Indian.
```{r }

netflix_cast= netflix_data %>%
  mutate(cast=gsub("^(.*?),.*", "\\1", cast)) %>% 
  filter(type=="Movie" & nchar(cast)!=0 ) %>%
  group_by(cast,country) %>% 
  count() %>%
  summarize(total_count=sum(n)) %>%
  arrange(desc(total_count)) %>%
  head(5)

netflix_cast

``` 


```  {r }

# Which Date , Which Cast
netflix_cast_by_year = netflix_data %>% 
  mutate(cast=gsub("^(.*?),.*", "\\1", cast)) %>% 
  filter(type=="Movie" & nchar(cast)!=0 ) %>%
  group_by(cast,release_year) %>% count() %>%
  arrange(desc(cast,release_year))


netflix_cast_by_year2= netflix_director_by_year %>% inner_join(netflix_cast,by="cast")
netflix_cast_by_year2
``` 

 
 Let's see the grap
 
```  {r } 

netflix_cast

ggplot(netflix_cast_by_year2,aes(x=release_year,y=n,color=cast)) + 
  geom_point() + 
  labs(title="Yıllara Göre Oyuncuların Film Sayısı",caption="Source: Netflix") +
  expand_limits(y=0)

``` 
 
To be continued.....




Thanks for Yigit Erol’s [Medium](https://medium.com/deep-learning-turkiye/exploration-of-netflix-2020-dataset-in-r-markdown-eda-b202bbaec4a)




